Accuracy and precision of zero-heat-flux temperature measurements with the 3M^TM^ Bair Hugger^TM^ Temperature Monitoring System

### 2020-05-20 manuscript/manuscript.Rmd
R2 for JCMC

data_NPA <- data %>% 
  dplyr::filter(comparison == "NPA")

data_SL <- data %>% 
  dplyr::filter(comparison == "Sublingual")

#eshragi overall
data_core <- data %>% 
  dplyr::filter(comparison=="PA"|comparison=="Bladder"|comparison=="Eso" | comparison =="Rectal"|comparison =="Ax"|comparison =="Iliac") %>%
  dplyr::filter(comments != "Intraoperative, off cardiopulmonary bypass" & comments != "Postoperative")

@@

data_core_op <- data %>% #eshragi intraop
    dplyr::filter(comparison=="PA"|comparison=="Bladder"|comparison=="Eso" | comparison =="Rectal"|comparison =="Ax"|comparison =="Iliac") %>%
  dplyr::filter (clinical_setting=="Intraoperative")

data_core_icu <- data %>% #eshragi postop
      dplyr::filter(comparison=="PA"|comparison=="Bladder"|comparison=="Eso" | comparison =="Rectal"|comparison =="Ax"|comparison =="Iliac") %>%
  dplyr::filter(clinical_setting=="ICU" | clinical_setting=="Postoperative")

@@

```{r NPA, include=FALSE}
NPA  <- format_results(data_NPA)
```

```{r SL, include=FALSE}
SL  <- format_results(data_SL)
```

@@

Eighteen studies were included. The primary meta-analysis of zero-heat-flux versus core temperature consisted of `r primary$Comparisons` comparisons from `r primary$Studies` individual studies. Data from `r primary$Participants` participants with `r format(primary$Measurements, scientfic=F)` paired measurements were included. The pooled estimate for the mean bias was `r primary$bias_mean`°C. Population limits of agreement, which take into consideration the between-study heterogeneity and sampling error, were wide, spanning from `r primary$CI_L_rve`°C to `r primary$CI_U_rve`°C. The GRADE evidence quality rating was downgraded to moderate due to concerns about study limitations. Population limits of agreement for the sensitivity analysis restricted to studies rated as having low risk of bias across all the domains of the QUADAS-2 were similar to the primary analysis.

@@

A systematic review was conducted. The primary comparison for this review was zero-heat-flux temperature measured using the 3M^TM^ Bair Hugger^TM^ Temperature Monitoring System versus temperature measured from a core site, which we defined as temperature measured at either an arterial, esophageal, bladder or rectal site. Secondary comparisons were made between temperatures measured using the 3M^TM^ Bair Hugger^TM^ Temperature Monitoring System and temperatures taken at peripheral sites.

@@

Measures of uncertainty were included in our meta-analyses by calculating the outer 95% confidence intervals for pooled limits of agreement. We also accounted for repeated measurements if they were not properly adjusted for in individual studies. This was achieved by using weights proportional to the number of participants, not the total number of measurements.  The R statistical program was used to conduct all analyses.[@R2018] All data and R code used in the meta-analyses is available [here](https://github.com/awconway/zhf-review).

Prior to conducting the meta-analyses, the results from each study were converted into a standard format, with bias meaning comparator thermometer temperature measurement minus the 3M^TM^ Bair Hugger^TM^ Temperature Monitoring System measurement in degrees Celsius (°C). In several studies, results were reported for multiple groups of participants, therefore in the meta-analysis each of these groups was treated as a separate 'comparison'.[@Boisson_2018; @Dahyot_Fizelier_2017; @Schell_Chaple_2018; @M_kinen_2016] Other studies reported multiple sets of results, whereby analyses were conducted between zero-heat-flux and various comparator devices used on the same participant. These instances were also treated as a separate 'comparison' if the comparator devices were a part of separate meta-analysis groups.[@West_2019; @Pesonen_2018; @M_kinen_2016; @Iden_2015] One study reported intraoperative, postoperative and overall results for the same participants[@eshraghi2014]. Only the paired measurements from the overall results were included in the main and low risk bias analyses, leaving paired measurements exclusively from the intraoperative and postoperative timepoints to be included in respective meta-analyses subgroups.

The conventionally cited clinically acceptable agreement between zero-heat-flux and comparator devices is 0.5°C.[@eshraghi2014] It was deemed that outer confidence bounds for 95% limits of agreement between zero-heat-flux and core temperature measurements (termed as ‘population limits of agreement’) outside of these bounds would be clinically unacceptable.

A sensitivity analysis for the primary comparison (zero-heat-flux versus temperature measurement at core site) was performed based on risk of bias, whereby ‘unclear risk of bias’ was treated as ‘high risk’ and ‘high risk of bias’ studies were excluded from analyses. We also conducted a sensitivity analysis for the primary comparison (zero-heat-flux versus temperature measurement at core site) excluding studies that received funding from industry. As clinicians would be interested in the accuracy of zero-heat-flux relative within the clinical setting in which they use it, we conducted subgroup analyses for the primary comparison according to clinical setting of the study (either intraoperative or intensive care unit).

@@

A summary of the characteristics of included studies is displayed in Table 1. The primary comparison of the 3M^TM^ Bair Hugger^TM^ Temperature Monitoring System versus core temperature measurements (eg, arterial, bladder, esophageal or rectal) consisted of `r primary$Comparisons` comparisons from `r primary$Studies` individual studies.[@Boisson_2018; @Carvalho_2019; @Dahyot_Fizelier_2017; @eshraghi2014; @G_mez_Romero_2019; @idei2016; @Jack_2019; @Kato_2015; @kollmann2019validation; @M_kinen_2016; @Morettini_2019; @Pesonen_2018; @Schell_Chaple_2018; @Tachibana_2019] In total, data from `r primary$Participants` participants with `r format(primary$Measurements, scientfic=F)` paired measurements were included in this comparison (two studies did not report the total number of measurements included in their analysis). The sensitivity analysis for the primary comparison with only studies that were assessed as low risk of bias across all domains included `r low_risk$Comparisons` comparisons from `r low_risk$Studies` studies that enrolled `r low_risk$Participants` participants with `r low_risk$Measurements` paired measurements (two studies did not report the total number of measurements included in their analysis). There were `r ICU$Studies` studies that compared zero-heat-flux to core temperature measurements in ICU patients, comprising `r ICU$Comparisons` comparisons with `r ICU$Measurements` measurements from `r ICU$Participants` participants. Another `r OT$Studies` studies were included that compared zero-heat-flux to core temperature measurements in patients undergoing surgery, comprising `r OT$Comparisons` comparisons with `r OT$Measurements` measurements from `r OT$Participants` participants. Nasopharyngeal thermometers were used as the comparator devices in `r NPA$Studies` studies, with `r NPA$Measurements` paired measurements from `r NPA$Participants` participants. Sublingual thermometers were used as the comparator devices in `r SL$Studies` studies that reported `r SL$Measurements` paired measurements from `r SL$Participants` participants. Supplementary information presented in the study [webpage](https://zhf-info.netlify.app) provides comprehensive summaries of the studies included in each of these meta-analyses.

@@

### Primary comparison: 3M^TM^ Bair Hugger^TM^ Temperature Monitoring System versus core thermometers

Table 2 presents results of the primary, sensitivity and all subgroup analyses for the primary comparison as well as secondary comparisons. The pooled estimate for the mean bias between the 3M^TM^ Bair Hugger^TM^ Temperature Monitoring System and core temperature measurements was `r primary$bias_mean`°C. Population limits of agreement, which take into consideration the between-study heterogeneity and sampling error, were wide, spanning from `r primary$CI_L_rve`°C to `r primary$CI_U_rve`°C (`r primary$Measurements` measurements; `r primary$Participants` participants; `r primary$Studies` studies). The amount of between-study heterogeneity is displayed graphically in the density plot in Figure 3. The quality of evidence for the primary comparison was downgraded to moderate quality due to concerns about study limitations. Population limits of agreement for the sensitivity analysis restricted to studies rated as having low risk of bias across all the domains of the QUADAS-2 were similar to the primary analysis (`r low_risk$Measurements` measurements; `r low_risk$Participants` participants; `r low_risk$Studies` studies). The mean bias was again `r low_risk$bias_mean`°C with population limits of agreement spanning from `r low_risk$CI_L_rve`°C to `r low_risk$CI_U_rve`°C. A further sensitivity analysis excluding studies that received industry funding revealed population limits of agreement that were considerably wider than the primary analysis (`r conflict$CI_L_rve`°C to `r conflict$CI_U_rve`°C). The evidence rating for this sensitivity analysis was downgraded to low quality though, due to concerns about study limitations, inconsistency and imprecision.

@@

### Secondary comparisons: 3M^TM^ Bair Hugger^TM^ Temperature Monitoring System versus peripheral thermometers

Temperature measurements from the 3M^TM^ Bair Hugger^TM^ Temperature Monitoring System  were compared with sublingual and nasopharyngeal temperature measurements in several studies included in this review. The mean bias between 3M^TM^ Bair Hugger^TM^ Temperature Monitoring System and nasopharyngeal temperature measurements in meta-analysis of results from `r NPA$Studies` studies was `r NPA$bias_mean`°C. Population limits of agreement were `r NPA$CI_L_rve`°C to `r NPA$CI_U_rve`°C. We downgraded the quality of evidence to low, again due to concerns about imprecision and study limitations. The mean bias between the 3M^TM^ Bair Hugger^TM^ Temperature Monitoring System and sublingual temperature measurements in meta-analysis of results from `r SL$Studies` studies was `r SL$bias_mean`°C. Due to the limited number of studies and measurements, population limits of agreement were extremely wide, spanning outside physiologically plausible range for temperature. As such, they are not reported.  The quality of evidence for this comparison was rated as very low quality due to serious concerns about imprecision.

@@

This systematic review showed that a temperature measurement from a 3M^TM^ Bair Hugger^TM^ Temperature Monitoring System device could be as much as 1°C higher or lower than core temperature. These results may have important implications for practice. It was reassuring that results of our sensitivity analysis restricted to studies assessed to be at low risk of bias using the QUADAS-2 tool were similar. As such, it is vital for healthcare professionals considering using this device to first determine if differences in temperature smaller than this magnitude would be important for the given clinical situation. If so, then it may not be appropriate to substitute the 3M^TM^ Bair Hugger^TM^ Temperature Monitoring System in place of a core thermometer.

@@

Subgroup analyses revealed insights to direct future research. There were fewer participants included in the subgroup of studies conducted in the Intensive Care Unit compared to those conducted during surgery. As a result, population limits of agreement for the Intensive Care Unit subgroup were broad. Additional studies are required to increase confidence in the accuracy of 3M^TM^ Bair Hugger^TM^ Temperature Monitoring System device in this setting, where continuous temperature monitoring is often required.

Although comparisons with core temperature are the most important to evaluate, we included studies that compared 3M^TM^ Bair Hugger^TM^ Temperature Monitoring System and peripheral temperature monitoring devices in our review because clinicians may be interested to determine if this new technology is sufficiently accurate to replace other ways to non-invasively monitor temperature. Also, there may be situations where it is standard practice for only peripheral temperature monitoring to be used. In these circumstances, it is not practical to expose research participants to the potential risks of invasive core temperature monitoring for the purpose of evaluating the new temperature monitoring device. Whether or not the zero-heat-flux thermometer is sufficiently accurate to be used in place of nasopharyngeal thermometers is unclear. Population limits of agreement calculated from four studies were broad, spanning from 1°C less than zero-heat-flux temperature to one degree higher. Further studies are therefore required.

@@

The accuracy of 3M^TM^ Bair Hugger^TM^ Temperature Monitoring System has been evaluated in various intraoperative contexts as well as in the intensive care unit setting. Our subgroup analyses did not indicate that the accuracy of this temperature monitoring device was any more effective in a particular setting. Only two studies included in our systematic review included pediatric patients. Additional studies to evaluate the accuracy of this device in children may be warranted to increase confidence.

@@

We did not extract data on adverse events due to temperature monitoring with the 3M^TM^ Bair Hugger^TM^ Temperature Monitoring System. The possibility of publication bias cannot be ruled out, although the evidence suggests this may not be as serious of a problem for studies that are not randomized controlled trials.[@begg2005systematic] Our focus for the meta-analysis was on calculating population limits of agreement, which incorporate the variation in bias between studies into the estimates. For this reason, we did not use meta-regression or tests for interaction between subgroups as a way to investigate sources of heterogeneity. It is important to note that this review did not assess the clinical utility of temperature monitoring using the zero-heat-flux device. The evidence from this review should be considered in the context of other information about the reliability and ease of use of this device. For example, the 3M^TM^ Bair Hugger^TM^ Temperature Monitoring System permits use of the same temperature monitoring device to be used throughout the whole perioperative care pathway. As such, use of this device during the pre and post-operative period to replace indirect estimates of core temperature, such as infrared tympanic and temporal devices, which are not recommended for use in surgical patients[@riley2018inadvertent] yet are commonly used because of convenience, may be an advantage.

@@

```{r }
data_NPA <- gofer::data_NPA
data_SL <- gofer::data_SL
data_core <- gofer::data_core
data_NPA$comparison <- sub("NPA", "Nasopharyngeal", data_NPA$comparison) 
data_NPA$Study <- sub("West, 2018", "West, 2019", data_NPA$Study)

data_core$comparison <- sub("PA", "Pulmonary artery", data_core$comparison) 
data_core$comparison <- sub("Iliac", "Iliac artery", data_core$comparison) 
data_core$comparison <- sub("Ax", "Axillary artery", data_core$comparison) 
data_core$comparison <- sub("Eso", "Esophageal", data_core$comparison)
data_core$patients <- sub("Gynecological Surgery", "Gynecology Surgery", data_core$patients)
data_core$patients <- sub("Laparosopic Surgery", "Laparoscopy Surgery", data_core$patients)

data_NPA_age <- gofer::data_NPA_age
data_NPA_age$Study <- sub("West, 2015", "West, 2019", data_NPA_age$Study)

data_NPA <- data_NPA_age %>% 
  tidyr::pivot_wider(names_from = c(age_type, age_measure),
                    values_from = age) %>% 
  dplyr::rename(mean_age = mean_sd_average,
         lower_mean = mean_sd_lower,
         upper_mean = mean_sd_upper,
         median_age = median_iqr_average,
         lower_IQR = median_iqr_lower,
         upper_IQR = median_iqr_upper) %>% 
  left_join(data_NPA)

data_SL_age <- gofer::data_SL_age
data_SL_age$Study <- sub("West, 2015", "West, 2019", data_SL_age$Study)

data_SL$Study <- sub("West, 2018", "West, 2019", data_SL$Study)

data_SL <- data_SL_age %>% 
  tidyr::pivot_wider(names_from = c(age_type, age_measure),
                    values_from = age) %>% 
  dplyr::rename(mean_age = mean_sd_average,
         lower_mean = mean_sd_lower,
         upper_mean = mean_sd_upper,
         median_age = median_iqr_average,
         lower_IQR = median_iqr_lower,
         upper_IQR = median_iqr_upper) %>% 
  left_join(data_SL)

ft <- data_core %>% 
    dplyr::bind_rows(data_SL) %>%
      dplyr::bind_rows(data_NPA) %>%
    dplyr::arrange(Study) %>% 
    tidyr::separate(Study, c("Study", "Year"), sep = ", ")  %>% 
  dplyr::arrange(-as.numeric(Year)) %>% 
       dplyr::mutate(perc_male = round((male/(female+male))*100, 1)) %>% 
  dplyr::mutate(N= tidyr::replace_na(N, 0)) %>% 
    dplyr::mutate(age = ifelse(!is.na(mean_age), 
                      glue::glue("{mean_age} ({mean_age - lower_mean})"),
                      glue::glue("{median_age} [{lower_IQR}-{upper_IQR}]"))) %>% 
    dplyr::mutate(temp_range = glue::glue("{lower_temp}-{upper_temp}")) %>%
    dplyr::mutate(n1=n) %>% 
  dplyr::mutate(N1=N) %>% 
     dplyr::select(Year, Study, code, patients, perc_male, age, comparison, n,n1, N,N1, 
           temp_range) %>%
      flextable()

@@

```{r tab.style='table-flex'}
  ma <- list(primary, low_risk, ICU, OT,  NPA,SL, conflict)
names(ma) <- c("Primary", "Low risk studies", "Intensive Care Unit", 
               "Surgery", "Nasopharyngeal", "Sublingual",
               "Studies not funded by industry")
df <- dplyr::bind_rows(ma, .id="Comparison")

>>>>

data_NPA <- data %>% 
  dplyr::filter(comparison == "NPA")
# 
# data_SL <- data %>% 
#   dplyr::filter(comparison == "Sublingual")

#eshragi overall

data_core <- data %>% 
    dplyr::filter(comparison=="PA"|
                    comparison=="Bladder"|
                    comparison=="Eso" | 
                    comparison =="Rectal"|
                    comparison =="Ax"|
                    comparison =="Iliac" | 
                    comparison == "NOPA" |
                    (Study=="Iden, 2015"& comparison == "NPA")) %>%
  dplyr::filter(comments != "Intraoperative, off cardiopulmonary bypass" & comments != "Postoperative")

data_core_no_npa <- data %>% 
  dplyr::filter(comparison=="PA"|comparison=="Bladder"|comparison=="Eso" | comparison =="Rectal"|comparison =="Ax"|comparison =="Iliac") %>%
  dplyr::filter(comments != "Intraoperative, off cardiopulmonary bypass" & comments != "Postoperative")

@@

data_core_op <- data %>% #eshragi intraop
    dplyr::filter(comparison=="PA"|comparison=="Bladder"|comparison=="Eso" | comparison =="Rectal"|comparison =="Ax"|comparison =="Iliac"|
                                        comparison == "NOPA" |
                    (Study=="Iden, 2015"& comparison == "NPA")) %>%
  dplyr::filter (clinical_setting=="Intraoperative")

data_core_icu <- data %>% #eshragi postop
      dplyr::filter(comparison=="PA"|comparison=="Bladder"|comparison=="Eso" | comparison =="Rectal"|comparison =="Ax"|comparison =="Iliac" |
                                          comparison == "NOPA" |
                    (Study=="Iden, 2015"& comparison == "NPA")) %>%
  dplyr::filter(clinical_setting=="ICU" | clinical_setting=="Postoperative")

@@

```{r NPA, include=FALSE}
NPA  <- format_results(data_NPA)
core_no_npa <- format_results(data_core_no_npa)
```

```{r SL, include=FALSE}
# SL  <- format_results(data_SL)
```

@@

Sixteen studies were included. The primary meta-analysis of zero-heat-flux versus core temperature consisted of `r primary$Comparisons` comparisons from `r primary$Studies` individual studies. Data from `r primary$Participants` participants with `r format(primary$Measurements, scientfic=F)` paired measurements were included. The pooled estimate for the mean bias was `r primary$bias_mean`°C. Population limits of agreement, which take into consideration the between-study heterogeneity and sampling error, were wide, spanning from `r primary$CI_L_rve`°C to `r primary$CI_U_rve`°C. The GRADE evidence quality rating was downgraded to moderate due to concerns about study limitations. Population limits of agreement for the sensitivity analysis restricted to studies rated as having low risk of bias across all the domains of the QUADAS-2 were similar to the primary analysis.

@@

A systematic review was conducted. The primary comparison for this review was zero-heat-flux temperature measured using the 3M^TM^ Bair Hugger^TM^ Temperature Monitoring System versus temperature measured from a core site, which we defined as temperature measured at either an arterial, esophageal, bladder, rectal, nasopharyngeal or oropharyngeal site.

@@

Measures of uncertainty were included in our meta-analyses by calculating the outer 95% confidence intervals for pooled limits of agreement. We also accounted for repeated measurements if they were not properly adjusted for in individual studies. This was achieved by using weights proportional to the number of participants, not the total number of measurements.  The R statistical program was used to conduct all analyses.[@R2018] All data and R code used in the meta-analyses is available [here](https://github.com/awconway/zhf-review) and archived [here](https://doi.org/10.5281/zenodo.3817610).

Prior to conducting the meta-analyses, the results from each study were converted into a standard format, with bias meaning comparator thermometer temperature measurement minus the 3M^TM^ Bair Hugger^TM^ Temperature Monitoring System measurement in degrees Celsius (°C). In several studies, results were reported for multiple groups of participants, therefore in the meta-analysis each of these groups was treated as a separate 'comparison'.[@Boisson_2018; @Dahyot_Fizelier_2017; @Schell_Chaple_2018; @M_kinen_2016] Other studies reported multiple sets of results, whereby analyses were conducted between zero-heat-flux and various comparator devices used on the same participant. These instances were also treated as a separate 'comparison' if the comparator devices were a part of separate meta-analysis groups.[@West_2019; @Pesonen_2018; @M_kinen_2016; @Iden_2015] One study used both nasopharyngeal and oropharyngeal temperature as comparators.[@West_2019] Both combined and separate estimates were reported. We used the combined estimate in our primary analysis and the estimate for just the nasopharyngeal temperatures in a subgroup analysis.  One study reported intraoperative, postoperative and overall results for the same participants[@eshraghi2014]. Only the paired measurements from the overall results were included in the main and low risk bias analyses, leaving paired measurements exclusively from the intraoperative and postoperative timepoints to be included in respective meta-analyses subgroups. 
The conventionally cited clinically acceptable agreement between zero-heat-flux and comparator devices is 0.5°C.[@eshraghi2014] It was deemed that outer confidence bounds for 95% limits of agreement between zero-heat-flux and core temperature measurements (termed as ‘population limits of agreement’) outside of these bounds would be clinically unacceptable.

A sensitivity analysis for the primary comparison (zero-heat-flux versus temperature measurement at core site) was performed based on risk of bias, whereby ‘unclear risk of bias’ was treated as ‘high risk’ and ‘high risk of bias’ studies were excluded from analyses. We also conducted a sensitivity analysis for the primary comparison (zero-heat-flux versus temperature measurement at core site) excluding studies that received funding from industry.  Probe insertion distance for temperature measurements from the nasopharynx and oropharynx may impact accuracy.[@Lim_2016] For this reason, we also conducted a separate analysis excuding these comparators and an analysis of the studies that compared temperature measurements from the 3M^TM^ Bair Hugger^TM^ Temperature Monitoring System with nasopharyngeal temperature. As clinicians would be interested in the accuracy of zero-heat-flux relative within the clinical setting in which they use it, we conducted subgroup analyses for the primary comparison according to clinical setting of the study (either intraoperative or intensive care unit).

@@

A summary of the characteristics of included studies is displayed in Table 1. The primary comparison of the 3M^TM^ Bair Hugger^TM^ Temperature Monitoring System versus core temperature measurements consisted of `r primary$Comparisons` comparisons from `r primary$Studies` individual studies.[@Boisson_2018; @Carvalho_2019; @Dahyot_Fizelier_2017; @eshraghi2014; @G_mez_Romero_2019; @idei2016; @Jack_2019; @Kato_2015; @kollmann2019validation; @M_kinen_2016; @Morettini_2019; @Pesonen_2018; @Schell_Chaple_2018; @Tachibana_2019; @West_2019; @Iden_2015] In total, data from `r primary$Participants` participants with `r format(primary$Measurements, scientfic=F)` paired measurements were included in this comparison (two studies did not report the total number of measurements included in their analysis). The sensitivity analysis for the primary comparison with only studies that were assessed as low risk of bias across all domains included `r low_risk$Comparisons` comparisons from `r low_risk$Studies` studies that enrolled `r low_risk$Participants` participants with `r low_risk$Measurements` paired measurements (two studies did not report the total number of measurements included in their analysis). There were `r ICU$Studies` studies that compared zero-heat-flux to core temperature measurements in ICU patients, comprising `r ICU$Comparisons` comparisons with `r ICU$Measurements` measurements from `r ICU$Participants` participants. Another `r OT$Studies` studies were included that compared zero-heat-flux to core temperature measurements in patients undergoing surgery, comprising `r OT$Comparisons` comparisons with `r OT$Measurements` measurements from `r OT$Participants` participants. Nasopharyngeal thermometers were used as the comparator devices in `r NPA$Studies` studies, with `r NPA$Measurements` paired measurements from `r NPA$Participants` participants. Supplementary information presented in the study [webpage](https://zhf-info.netlify.app) provides comprehensive summaries of the studies included in each of these meta-analyses.

@@

### Primary comparison

Table 2 presents results of the primary, sensitivity and all subgroup analyses. The pooled estimate for the mean bias between the 3M^TM^ Bair Hugger^TM^ Temperature Monitoring System and core temperature measurements was `r primary$bias_mean`°C. Population limits of agreement, which take into consideration the between-study heterogeneity and sampling error, were wide, spanning from `r primary$CI_L_rve`°C to `r primary$CI_U_rve`°C (`r primary$Measurements` measurements; `r primary$Participants` participants; `r primary$Studies` studies). The amount of between-study heterogeneity is displayed graphically in the density plot in Figure 3. The quality of evidence for the primary comparison was downgraded to moderate quality due to concerns about study limitations.

### Sensitivity analyses

Population limits of agreement for the sensitivity analysis restricted to studies rated as having low risk of bias across all the domains of the QUADAS-2 were similar to the primary analysis (`r low_risk$Measurements` measurements; `r low_risk$Participants` participants; `r low_risk$Studies` studies). The mean bias was again `r low_risk$bias_mean`°C with population limits of agreement spanning from `r low_risk$CI_L_rve`°C to `r low_risk$CI_U_rve`°C. A further sensitivity analysis excluding studies that received industry funding revealed population limits of agreement that were considerably wider than the primary analysis (`r conflict$CI_L_rve`°C to `r conflict$CI_U_rve`°C). The evidence rating for this sensitivity analysis was downgraded to low quality though, due to concerns about study limitations, inconsistency and imprecision.

To investigate if results were sensitive to our decision about which  temperature monitoring sites to include in the primary analysis, we conducted a separate analysis excluding any naso/oropharyngeal comparisons. Results were similar to the primary analysis (`r glue::glue("mean bias {core_no_npa$bias_mean}°C with population limits of agreement from {core_no_npa$CI_L_rve} to {core_no_npa$CI_U_rve}°C)")`. The mean bias between 3M^TM^ Bair Hugger^TM^ Temperature Monitoring System and nasopharyngeal temperature measurements in meta-analysis of results from `r NPA$Studies` studies was `r NPA$bias_mean`°C. Population limits of agreement were `r NPA$CI_L_rve`°C to `r NPA$CI_U_rve`°C. We downgraded the quality of evidence to low, again due to concerns about imprecision and study limitations.

## Subgroup analyses

@@

@@

This systematic review showed that a temperature measurement from a 3M^TM^ Bair Hugger^TM^ Temperature Monitoring System device could be as much as about 1°C higher or lower than core temperature. These results may have important implications for practice. It was reassuring that results of our sensitivity analysis restricted to studies assessed to be at low risk of bias using the QUADAS-2 tool were similar. As such, it is vital for healthcare professionals considering using this device to first determine if differences in temperature smaller than this magnitude would be important for the given clinical situation. If so, then it may not be appropriate to substitute the 3M^TM^ Bair Hugger^TM^ Temperature Monitoring System in place of a core thermometer.

@@

The accuracy of 3M^TM^ Bair Hugger^TM^ Temperature Monitoring System has been evaluated in various intraoperative contexts as well as in the intensive care unit setting. Our subgroup analyses did not indicate that the accuracy of this temperature monitoring device was any more effective in a particular setting and revealed insights to direct future research. There were fewer participants included in the subgroup of studies conducted in the Intensive Care Unit compared to those conducted during surgery. As a result, population limits of agreement for the Intensive Care Unit subgroup were broad. Additional studies are required to increase confidence in the accuracy of 3M^TM^ Bair Hugger^TM^ Temperature Monitoring System device in this setting, where continuous temperature monitoring is often required. Also of note, only two studies included in our systematic review included pediatric patients. Additional studies to evaluate the accuracy of this device in children may be warranted to increase confidence.

@@

@@

We did not extract data on adverse events due to temperature monitoring with the 3M^TM^ Bair Hugger^TM^ Temperature Monitoring System. The possibility of publication bias cannot be ruled out, although the evidence suggests this may not be as serious of a problem for studies that are not randomized controlled trials.[@begg2005systematic] Our focus for the meta-analysis was on calculating population limits of agreement, which incorporate the variation in bias between studies into the estimates. For this reason, we did not use meta-regression or tests for interaction between subgroups as a way to investigate sources of heterogeneity. It is important to note that this review did not assess the clinical utility of temperature monitoring using the zero-heat-flux device. The evidence from this review should be considered in the context of other information about the reliability and ease of use of this device. For example, the 3M^TM^ Bair Hugger^TM^ Temperature Monitoring System permits use of the same temperature monitoring device to be used throughout the whole perioperative care pathway. As such, replacing indirect estimates of core temperature, such as infrared tympanic and temporal devices, may be an advantage of the 3M^TM^ Bair Hugger^TM^ Temperature Monitoring System. Indirect estimates of core temperature are not recommended for use in surgical patients, yet are commonly used because of convenience.[@riley2018inadvertent]

@@

```{r }
# data_NPA <- gofer::data_NPA
# data_SL <- gofer::data_SL
data_core <- gofer::data_core
# data_NPA$comparison <- sub("NPA", "Nasopharyngeal", data_NPA$comparison) 
# data_NPA$Study <- sub("West, 2018", "West, 2019", data_NPA$Study) 
data_core$comparison <- sub("NPA", "Nasopharyngeal", data_core$comparison) 
data_core$comparison <- sub("NOPA", "Naso or oropharyngeal", data_core$comparison)
data_core$comparison <- sub("PA", "Pulmonary artery", data_core$comparison) 
data_core$comparison <- sub("Iliac", "Iliac artery", data_core$comparison) 
data_core$comparison <- sub("Ax", "Axillary artery", data_core$comparison) 
data_core$comparison <- sub("Eso", "Esophageal", data_core$comparison)
data_core$patients <- sub("Gynecological Surgery", "Gynecology Surgery", data_core$patients)
data_core$patients <- sub("Laparosopic Surgery", "Laparoscopy Surgery", data_core$patients)

# data_NPA_age <- gofer::data_NPA_age
# data_NPA_age$Study <- sub("West, 2015", "West, 2019", data_NPA_age$Study) 
# 
# data_NPA <- data_NPA_age %>% 
#   tidyr::pivot_wider(names_from = c(age_type, age_measure),
#                     values_from = age) %>% 
#   dplyr::rename(mean_age = mean_sd_average,
#          lower_mean = mean_sd_lower,
#          upper_mean = mean_sd_upper,
#          median_age = median_iqr_average,
#          lower_IQR = median_iqr_lower,
#          upper_IQR = median_iqr_upper) %>% 
#   left_join(data_NPA) 
# 
# data_SL_age <- gofer::data_SL_age
# data_SL_age$Study <- sub("West, 2015", "West, 2019", data_SL_age$Study) 
# 
# data_SL$Study <- sub("West, 2018", "West, 2019", data_SL$Study) 
# 
# data_SL <- data_SL_age %>% 
#   tidyr::pivot_wider(names_from = c(age_type, age_measure),
#                     values_from = age) %>% 
#   dplyr::rename(mean_age = mean_sd_average,
#          lower_mean = mean_sd_lower,
#          upper_mean = mean_sd_upper,
#          median_age = median_iqr_average,
#          lower_IQR = median_iqr_lower,
#          upper_IQR = median_iqr_upper) %>% 
#   left_join(data_SL)

ft <- data_core %>% 
    # dplyr::bind_rows(data_SL) %>%
    #   dplyr::bind_rows(data_NPA) %>%
    dplyr::arrange(Study) %>% 
    tidyr::separate(Study, c("Study", "Year"), sep = ", ")  %>% 
  dplyr::arrange(-as.numeric(Year)) %>% 
       dplyr::mutate(perc_male = round((male/(female+male))*100, 1)) %>% 
  dplyr::mutate(N= tidyr::replace_na(N, 0)) %>% 
    dplyr::mutate(age = ifelse(!is.na(mean_age), 
                      glue::glue("{mean_age} ({mean_age - lower_mean})"),
                      glue::glue("{median_age} [{lower_IQR}-{upper_IQR}]"))) %>% 
    dplyr::mutate(temp_range = glue::glue("{lower_temp}-{upper_temp}")) %>%
    dplyr::mutate(n1=n) %>% 
  dplyr::mutate(N1=N) %>% 
     dplyr::select(Year, Study, code, patients, perc_male, age, comparison, n,n1, N,N1, 
           temp_range) %>%
      flextable()

@@

```{r tab.style='table-flex'}
  ma <- list(primary, low_risk,core_no_npa, NPA, conflict, ICU, OT)
names(ma) <- c("Primary", 
               "Low risk studies",  
               "Core (excluding nasopharyngeal and oropharyngeal)", 
               "Nasopharyngeal", 
               "Studies not funded by industry",
               "Intensive Care Unit", 
               "Surgery")
df <- dplyr::bind_rows(ma, .id="Comparison")

df %>%
  rename(" " = Comparison, "Mean bias" = bias_mean,
         "Tau-squared" = tau_est, 
         "Lower 95% LoA" = LOA_L, 
         "Upper 95% LoA" = LOA_U, 
         "Outer CI for lower 95% LoA" = CI_L_rve, 
         "Outer CI for upper 95% LoA" = CI_U_rve) %>% flextable() %>% 
  compose(j=~sd2_est, part = "header",
          value = as_paragraph(
            "SD",
            as_sup("2")
          )) %>% 
  compose(j="Tau-squared", part = "header",
          value = as_paragraph(
            "τ",
            as_sup("2")
          ))  %>% 
  footnote(i = 1, j = 6:12,
               value = as_paragraph(
                "Units are °C"
               ),
               ref_symbols = "a",
               part = "header") %>% 
        footnote(i = 1, j = 7,
               value = as_paragraph(
                "Variance"
               ),
               ref_symbols = "b",
               part = "header") %>% 
    footnote(i = 1, j = 8,
               value = as_paragraph(
                "Measure of heterogeneity"
               ),
               ref_symbols = "c",
               part = "header") %>% 
    footnote(i = 1, j = 9:12,
               value = as_paragraph(
                "LoA = Limits of Agreement"
               ),
               ref_symbols = "d",
               part = "header") %>% 
    footnote(i = 1, j = 11:12,
               value = as_paragraph(
                "CI = Confidence Intervals"
               ),
               ref_symbols = "e",
               part = "header") %>% 
  add_header_row(values = c("","","","","","","","","","", "Population LoA"),  colwidths = c(rep(1,10, by=1), 2))   %>% 
  theme_booktabs() %>% 
  width(j=1,width = 1.19) %>%
  width(j=2,width = 0.69) %>%
  width(j=3,width = 1.06) %>%
  width(j=4,width = 0.94) %>%
  width(j=5,width = 1.19) %>%
  width(j=6,width = 0.56) %>%
  width(j=7,width = 0.56) %>%
  width(j=8,width = 0.6) %>%
  width(j=9,width = 0.59) %>%
  width(j=10,width = 0.75) %>%
  width(j=11,width = 0.94) %>%
  width(j=12,width = 0.94) %>% 
  fontsize(size = 10)
